---
title: "PlAcER: Plastic Accumulation Estimation using R"
author: "Davi Castro-Tavares, Esteban Acevedo-Trejos & Jailson F. Moura"
date: "`r Sys.Date()`"
output: rmarkdown::html_document #html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Overview


## Installation
To install simply type in the R console
```ruby
install.packages('placer')
```

## Usage
Load data containing observations of precense and absence of plastic debris.   
```{r}
library("placer")
# data(ctern)
ctern %>% tbl_df %>% rmarkdown::paged_table()
```


Calculate the bootstrap prevalence probability of plastic based on a specific
number of samples. Then from the resampled data the 95% confidence intervals (CI)
are computed. To quantify the prevalence probability and the CI simply provide
the presence/absense data, the maximum number of sample sizes to test (default 300),
and the number of bootstrap simulations (default 1000) as:

```ruby
ternsci<-placer::plastic.ci(cterns$debris_presence, 300, 1000)
```

Plot the plastic preevalence probability and the confidence interval 
as function of sample size: 
```{r plots, echo=FALSE, fig.cap = "Add here the figure caption"}
library(knitr)    # For knitting document and include_graphics function
ternsci<-placer::plastic.ci(ctern$debris_presence, 30, 100)
placer::prevalence_plot(ternsci$prevprob,
ternsci$cidtf$N,
ternsci$cidtf$lower_ci,
ternsci$cidtf$upper_ci)
```

## References
